The Effect of Void on the Cold Deformation Behaviour of $\alpha_2+\gamma$ Two Phase Ti-Al Alloy

### 2018-10-07 draft/alexpub.tex
no

% Full title of the paper (Capitalized)
% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
\Title{The Effect of Void on the}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology. Lanzhou 730050, China; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

\section{Introduction}
TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{vu2013}. Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}. Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator.

Deformation phenomena in TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance. The literature data covers a wide range of parameters such as alloy composition, microstructure and deformation temperature. Much of the work has been performed on single phase $\gamma$ alloys and PST crystals. 
% The failure modes of materials have significant influence on the design of material properties in materials science. 
Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{}. These defects are known to play a fundamental role in the deformation of the material. Nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important. Therefore, it is necessary to study the deformation response of porous materials with the consideration of microstructure evolution.

>>>>

% Full title of the paper (Capitalized)
% \Title{Effect of Nanovoid on Fracture Process of Two-Phase $\gamma$($\rm TiAl$)+$\alpha_2$($\rm Ti_3Al$) Alloy}
\Title{The Effect of Void on the Cold Deformation Behaviour of $\alpha_2+\gamma$ Two Phase Ti-Al Alloy}
% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0001-8385-4439} % Add \orcidA{} behind the author's name
\newcommand{\orcidauthorB}{0000-0002-9582-6301} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Ruicheng Feng $^{1,2}$\orcidA{}, Maomao Wang $^{1}$\orcidB{}}

% Authors, for metadata in PDF
%\AuthorNames{Maomao Wang $^{1,\dagger,\ddagger}$\orcidB{}, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad School of Mechanical and Electronical Engineering, Lanzhou University of Technology, Lanzhou 730050, China; frcly@163.com (R.F.); 15620864891@163.com (M.W.)\\
% $^{2}$ \quad Key Laboratory of Digital Manufacturing Technology and Application, Ministry of Education, Lanzhou University of Technology, Lanzhou 730050, China
%*; e-mail@e-mail.com}
$^{2}$ \quad State Key Laboratory of Advanced Processing and Recycling of Non-ferrous Metals, Lanzhou University of Technology, Lanzhou 730050, China}
% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: +x-xxx-xxx-xxxx}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

@@

\section{Introduction}
TiAl alloy has been used as structural material in aviation industry because its inherent advantages such as low density and self-diffusion rates, high elastic module and high strength \cite{vu2013}. Two-phase titanium aluminum alloys with proper phase distribution and grain size exhibit better mechanical performance compared with monolithic constituents $\gamma$(TiAl) and $\gamma$($\rm Ti_3Al$) alloy \cite{Kim1995}. Brittle fracture in TiAl alloy strongly affects the safety of fracture of structure like turbo of aircraft engine and combustion generator. Deformation phenomena of TiAl alloys have been widely studied in order to overcome the problems associated with the limited ductility and damage tolerance. A great number of literature covers a wide range of parameters such as alloy composition, microstructure and deformation temperature. Much of the work has been performed on single phase $\gamma$ alloys and PST crystals[]. 
% The failure modes of materials have significant influence on the design of material properties in materials science. 
Rapture failure at the macroscopic scale can be attributed to nucleation, growth and propagation of cracks, but at the microscopic scale cracks are initially easily formed at defects in the casting process, such as voids and inclusions \cite{}.

The initiation of crack at microscopic scale is a dynamic process, which resulting in difficulties on study of detailed mechanisms of defromation and cracking.

These defects are known to play a fundamental role in the deformation of the material. Nucleation, growth and coalescence of voids are deemed as the primary mechanism of ductile material fracture, in which void growth is particularly important. Therefore, it is necessary to study the deformation response of porous materials with the consideration of microstructure evolution.
